Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-12-16 R0V0.tex
Item 17
item 18

\mypara From the above steps, even if the problem of imposing a particular structure on $Y$ to correspond to the constraints of Problem \ref{problem formulation} was tractable, the integration of the controller would not necessarily satisfy these constraints. This is due to the fact that the solutions to the optimization problem \eqref{eq:geodesic formulation} can not be distributely computed.

\mypara In this paper, these limitations are addressed by imposing a block-diagonal structure over $W$.

>>>>

\mypara From the above steps, even if the problem of imposing a particular structure on $Y$ to correspond to the constraints of Problem \ref{problem formulation} was tractable, the integration of the controller would not necessarily satisfy these constraints. This is due to the fact that the solutions to the optimization problem \eqref{eq:geodesic formulation} cannot generally be computed in a distributed manner.

\mypara In this paper, these limitations are addressed by imposing a separable structure over $W$.
